Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-02-26 paper/snakemajoranas.tex
add acknowlegments

\author{Quantum Tinkerer}
\affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
\email[Electronic address: ]{quantumtinkerer@tudelft.nl}

@@

%%██████████████████████████████████████████████████████████████████████████
%%██ Acknowledgments
%%██████████████████████████████████████████████████████████████████████████
\section{Acknowledgments}
We are grateful to "people" for useful discussions.
This work was supported by the Netherlands Organization for Scientific Research (NWO/OCW), as part of the Frontiers of Nanoscience program, the Foundation for Fundamental Research on Matter (FOM), and an ERC Starting Grant STATOPINS 638760.

>>>>

\author{Tom Laeven}
\author{Bas Nijholt}
\author{Michael Wimmer}
\author{Anton R. Akhmerov}
\affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
\email[Electronic address: ]{quantumtinkerer@tudelft.nl}

@@

%%██████████████████████████████████████████████████████████████████████████
%%██ Acknowledgments
%%██████████████████████████████████████████████████████████████████████████
\section{Acknowledgments}
We are grateful to D. Varjas, T. Ö. Rosdahl, P. P. Piskunow, F. K. de Vries, S. Goswami, Q. Wang for useful discussions.
This work was supported by the Netherlands Organization for Scientific Research (NWO/OCW), as part of the Frontiers of Nanoscience program, a NWO VIDI Grant (SW), and an ERC Starting Grant STATOPINS 638760.
